The Spatial and Temporal Domains of Modern Ecology \\ OR Ecology's Spatio-temporal Domains\\ OR Space, Time, and Ecology \\ OR Ecology: still a small-scale, field-based discipline

### 2016-04-09 paper/main.tex
Added total title count and corrected sample percentage of this total

Given the importance of multi-scale studies for providing ecological understanding, and the growing ability to undertake them, it is important to rigorously assess whether ecology is becoming a multi-scale discipline. One approach to answering this question is to quantify the spatial and temporal domains within which observations in ecological studies are collected. Observations provide the necessary means for developing and testing the models that explain why ecological patterns vary in time and space \cite{levin_problem_1992,tilman_ecological_1989}, thus it stands to reason that the temporal and spatial range of ecological observations, and their density within different portions of those ranges, will shed light on modern ecology's progress towards a holistic, predictive understanding of ecosystems \cite{chave_problem_2013,levin_problem_1992}. In this study, we quantified the spatio-temporal domain of current ecological studies, using a representative sample of papers published between 2004-2014 in the top 30 ecological journals (by 2014 impact factor) to measure two key dimensions of spatial observation, resolution (grain) and total spatial extent, and their temporal corollaries, sampling interval and total temporal duration. We collected this information from 367 ecological observations (defined here as data collected from non-experimentally manipulated, or ``natural'' \cite{tilman_ecological_1989}, systems) reported within a 148 paper subset of 299 randomly selected articles (1.4\% of all papers).

>>>>

Given the importance of multi-scale studies for providing ecological understanding, and the growing ability to undertake them, it is important to rigorously assess whether ecology is becoming a multi-scale discipline. One approach to answering this question is to quantify the spatial and temporal domains within which observations in ecological studies are collected. Observations provide the necessary means for developing and testing the models that explain why ecological patterns vary in time and space \cite{levin_problem_1992,tilman_ecological_1989}, thus it stands to reason that the temporal and spatial range of ecological observations, and their density within different portions of those ranges, will shed light on modern ecology's progress towards a holistic, predictive understanding of ecosystems \cite{chave_problem_2013,levin_problem_1992}. In this study, we quantified the spatio-temporal domain of current ecological studies, using a representative sample of papers published between 2004-2014 in the top 30 ecological journals (by 2014 impact factor) to measure two key dimensions of spatial observation, resolution (grain) and total spatial extent, and their temporal corollaries, sampling interval and total temporal duration. We collected this information from 367 ecological observations (defined here as data collected from non-experimentally manipulated, or ``natural'' \cite{tilman_ecological_1989}, systems) reported within a 148 paper subset of 299 randomly selected articles (0.67\% of 44,346 papers).
